### 2016-08-28 paper.tex
Add explanation of stationary strut drag calcs

Measurements for the power coefficient contributions of the strut drag losses
are presented in Fig.~\ref{fig:no-blades} for NACA 0021 and cylindrical
struts---both in towed and stationary conditions. These are computed in the same
fashion as the curves in Fig.~\ref{fig:cp-curves}, but with the rotor blades
removed. We see that strut drag losses increase with tip speed ratio to the
power 2--3, which makes streamlined struts much more important for low solidity
turbines, given the inverse correlation between solidity and $\lambda_0$
\cite{Templin1974}.

@@

    \caption{{\bf Strut drag losses.} Measurements of the strut drag losses for
        (a) NACA 0021 and (b) cylindrical struts, both stationary and towed.}

>>>>

Measurements for the power coefficient contributions of the strut drag losses
are presented in Fig.~\ref{fig:no-blades} for NACA 0021 and cylindrical
struts---both in towed (at $U_\infty=1$ m/s) and stationary conditions. These
are computed in the same fashion as the curves in Fig.~\ref{fig:cp-curves}, but
with the rotor blades removed. For the stationary case, tip speed ratio and
power coefficient were computed using the same reference velocity $U_\infty=1$
m/s. We see that strut drag losses increase with tip speed ratio to the power
2--3, which makes streamlined struts much more important for low solidity
turbines, given the inverse correlation between solidity and $\lambda_0$
\cite{Templin1974}.

@@

    \caption{{\bf Strut drag losses.} Measurements of the strut drag losses for
    (a) NACA 0021 and (b) cylindrical struts, both stationary and towed at 1
    m/s. Note that stationary calculations for tip speed ratio and power
    coefficient also assumed $U_\infty = 1$ m/s.}
